Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
captian  updates

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase. SN mean RV seems to have the smallest spurious variations caused by the faculae.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{center}
\end{figure}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.  before and once corrected from stellar activity. \jessi{What is the correction done here?  I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.  Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
   %
 (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.  The residuals have a smaller systematic component when using the proposed model of 
  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star. In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RV's and the asymmetry parameter.}
    \label{fig:spot.corr}
\end{center}
\end{figure*}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase. SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{center}
\end{figure}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.  Before and once corrected from stellar activity. \jessi{What is the correction done here?  I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.  Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
   %
 (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.  The residuals have a smaller systematic component when using the proposed model of 
  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
   \caption{Using CCFs from SOAP 2.0 with a single spot, the correlation between the estimated RVs and the asymmetry or width parameters are displayed. In this case the shape changes with phase, producing statistically significant correlations between the estimated RVs and the asymmetry parameters (but not for the estimated RVs and the width parameters).}
    \label{fig:spot.corr}
\end{center}
\end{figure*}
